---
title: Making it go faster
author: Murray
date: '2019-05-24'
slug: furrr
categories:
  - R
tags:
  - R
  - parallel
  - purrr
  - furrr
---


Recently I have been going through some old code that I needed to rerun. As part of doing so I was taking the opportunity to reimplement it with some new tricks that I have discovered since I wrote it ~2 years ago.

This particular script has many, many `for` loops which I now wanted to replace with `purrr::map` to make the code cleaner and easier to maintain.

As part of using `purrr::map` I wondered if I could also make the code go faster by parallelising the loop. The short answer is yes, with the `furrr` package, using `furrr::future_map`.

The long answer comes from https://byuistats.github.io/M335/parallel_furrr.html

but in simplicity

```{r, eval = FALSE}
library(purrr)

purrr::map(list_object, function)

```

becomes:


```{r, eval = FALSE}
library(furrr)
no_cores <- availableCores() - 1
plan(multicore, workers = no_cores)

furrr::future_map(list_object, function)
```

where each item of the list if processed in parallel